The language of generalization: Probability, vagueness, and interaction

### 2018-10-23 paper/response.tex

In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainty.
That comment was meant in a very particular way relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}. 
We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
\textbf{Reviewer 1 also brings to our attention to property-based theories of concepts. We now are explicit---in the section on Intuitive Theories in the General Discussion---that the fact that our semantics is defined in terms of individual properties does not imply that the concepts involved in understanding generics are defined merely by their properties. Rather, complex intuitive theories, which can reflect conceptual role, produce prevalence priors which then yield generic judgments.}

### 2018-10-25 paper/response.tex

\begin{document}

\begin{letter}

\opening{Dear Professor Saxe,}

Thank you for soliciting peer reviews for our manuscript \emph{The Language of Generalization}. We appreciate the time both you and the reviewers have devoted to commenting and critiquing our manuscript. 
%We are greatly impressed by the depth and usefulness of all of the reviews.
We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
We have made a number of substantive changes in this version of the manuscript that we hope will improve the readability of the paper.

Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible, streamlined form,
we have merged the General Discussion subsection ``Other philosophical puzzles'' (e.g., \emph{Mary handles the mail from Antarctica}) with the examples that appeared before the experiments (e.g., \emph{birds lay eggs vs. are female}, \emph{mosquitos carry malaria}); now, both appear before the experiments in a section titled \emph{Worked Examples}.
We describe why each example is interesting, how the model handles each case, and provide a summary in a table (per R1's suggestion).
We elaborated the puzzle of ``Elephants live in Africa and Asia'' by adding a figure of the model predictions for this example.
We note in the worked examples when the relevant puzzle will be tested empirically (e.g., we now foreshadow the relevance of \emph{predictive probability} and motivate Expt. 2C using ``Supreme Court Justices have even social security numbers'').

We have taken Reviewers 1 and 3's suggestion of moving the \emph{Relationship to Other Semantic Theories} section to appear before the experiments (after the model section and worked examples).
We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theory to extant theories. 
Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with our model.
This is hopefully now more clearly articulated.

In the hope of addressing Reviewer 3's second comment, we include an additional subsection in the \emph{Relationship to Other Semantic Theories} section describing the various alternative quantitative models we will use for model comparison. 
The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our model is not overparameterized and that the prior in our model is not doing all of the work. 
This also allows us to clarify the sense in which our model is unique (R3's third comment): It is the first model of generics that makes quantitative predictions about human endorsements while connecting to a plausible truth-conditional semantic theory.

Reviewer 3 also made the more general comment that the presentation of material meanders in the paper. 
We agree and have added a brief \emph{Interim Summary and Overview of Experiments} section between the two halves of the paper (i.e., the model and related theories section vs. the experiments). 
This section summarizes the model, worked examples, and related theories and provides an overview of the experiments and the utility of each.
We also take Reviewer 1's criticism that the lay explanation of the model could be improved; we have added a short paragraph before the technical details of the model providing a high-level intuition for the model.
We hope these changes aid the readability.

We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
We have added a paragraph to the introductory remarks of the General Discussion about how accepting a generic sentence adds information about cue validity to the common ground, which suggests other empirical tests of our account.
We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
We have added a subsection to the General Discussion to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertain as to the exact truth conditions. 
We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is a kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity), which might point the way towards a more general information-theoretic typology of underspecification.
We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson and Simons (1992)'s epistemicist view.\footnote{
	R2 actually cited Williamson (1994). In our literature search, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons. 
}

In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
We have been more explicit in our discussion of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations.
We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainty.
That comment was meant in a very particular way relating to Leslie (2007, 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}. 
We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
Reviewer 1 also brought our attention to property-based theories of concepts. We now are explicit---in the section on Intuitive Theories in the General Discussion---that the fact that our semantics is defined in terms of individual properties does not imply that the concepts involved in understanding generics are defined merely by their properties. Rather, complex intuitive theories, which can reflect conceptual role, produce prevalence priors which then yield generic judgments.

### 2018-10-25 paper/comgen-paper.Rmd
final revisions for resubmission

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mhtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

@@

keywords          : "genericity, generalization, generics, pragmatics, semantics, Bayesian modeling"
wordcount         : "25000"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : no

@@

The paper is organized as follows. 
In the next section, we describe our computational framework for interpreting generalizations and our precise model for endorsing such statements (i.e., a model of truth judgments).
To illustrate how the model works, we then work through a number of standard examples from the linguistics literature that any model of generics should be able to accomodate.
The third section discusses the relationship of our model to previous accounts of generics from the linguistics and philosophical literatures. 
These introductory sections are followed by three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
In the case study of generics, we use measure relevant background knowledge and prevalence to predict endorsements of familiar generic statements (e.g., "Robins lay eggs").
In the study of habituals, we measure background knowledge but manipulate the prevalence or frequency of the event to predict endorsements of habitual statements about novel agents (e.g., "John runs" given that he's run a certain number of times in the past).
In this case study, we also further examine the nature of the relevant probabilities for endorsing generalizations, asking whether it matters how often John has run in the past (past frequency) or how often a speaker expects him to run in the future (predictive probability).
Finally, in our last case study, we manipulate background knowledge to show its causal influence on endorsing generalizations about novel causal events (e.g., "Herb X makes wugs sleepy"). 
We compare our model to two previously articulated quantitative models of generics as well as a lesioned-version of our model.
In all cases, we find a very strong agreement of our model's predictions to human elicited endorsements, where the simpler models fall short.
We conclude our paper by clarifying some of the theoretical claims of the model and discuss open-questions for this approach.

@@

The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "This dog has four legs").
In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
<!-- Dinosaurs are exctinct ~ John is a smoker? -->
Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Fire causes smoke"). 
Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We further distinguish the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]
We first describe a model for generics, before noting how the basic ideas generalize to habituals and causals.

@@

The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics.
The prevalence prior $P(p)$ is a distribution over probabilities $p$, which represents the output of a generative model of particular domain.
For properties of objects, the generative model is naturally a Bernoulli model (e.g., flipping a coin) and thus the support of $P(p)$ is $[0, 1]$.
For events, the implicit generative model is a Poisson model in which events occur randomly in time.
The probability density of an event occurring at a particular time is governed by the rate parameter for the Poisson model. 
Thus, Eq. \ref{eq:L0} becomes a model of habitual interpretation (e.g., "John runs") if we take the underlying semantic scale to be that of the temporal frequency of an event (e.g., how often we expect an event to occur); the support of $P(p)$ is this case would be $[0, \infty]$.

@@

<!-- The endorsement model defined in the previous section predicts that the variability in endorsements for generic statements and other sorts of generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq. \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq. \ref{eq:L0}). -->
We explore the predictions of the endorsement model in the context of a few worked examples.
These examples are taken from the linguistics literature on generics and are statements that have been historically challenging for prevalence-based approaches (see Table 1).
We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
All models, analyses, data and links to experiments used in this paper can be found at \url{https://mhtess.github.io}.

Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
\ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below}
\mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...}
The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
  Alternatively, the prevalence prior can be conceptualized as one aspect of an intuitive theory of a domain. 
]
<!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
We now turn our attention to the endorsement model's predictions.

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  Example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Robins lay eggs",
              "4. Robins are female",
              "5. Mosquitos carry malaria", 
              "6. Sharks don't eat people",
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "85%", "0 times", "100%", "50%/50%"),
  `intuitive truth value` = c(
    "True", "False",  "True", "False",
    "True", "False","True", "False", "True" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Only female robins (50%) lay eggs",
    "Same number that lay eggs (50%)",
    "Very few mosquitos actually carry malaria",
    "Most sharks don't eat people",
    "Consider there has never been any mail from Antarcita",
    "Consider 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia"
  )
) %>%
  rename("Referent prevalence" = referent.prevalence,
         "Intuitive truth value" = intuitive.truth.value,
         "Issue" = potential.issue)

worked.examples.tab <- xtable::xtable(worked.examples, 
                       caption = "Example sentences that a theory of generalizations should correctly predict. See details of each example in corresponding section.", 
                       align=c('| p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))

@@

## The role of conceptual knowledge

Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
It is this real-world knowledge (presently formalized in terms of a prevalence prior) where issues about domain specific knowledge, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
<!-- Instead,  -->
We hypothesize that all of this knowledge feeds into participants' predictions, measured through judgments about prevalence.
<!-- which we model in a precise, quantitative manner. -->
This framework, thus, brings precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work. 
Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.

@@

Conceptual knowledge concerning the strikingness or dangerousness of properties and their relation to generic language has been of particular interest to psychologists and philosophers since @Leslie2007.
We described before that the strikingness of certain properties plausibly influences prevalence priors or a speaker's predictions about future prevalence.
We have pilot data suggested these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
More empirical work is needed to understand whether and how strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.
<!-- If such effects exist, our modeling framework could be elaborated with a non-informational speaker utility [see e.g., @Yoon2016; @Yoon2017]. -->

>>>>

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "tessler@mit.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

@@

keywords          : "genericity, generalization, generics, pragmatics, semantics, Bayesian modeling"
wordcount         : "27578"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

@@

The paper is organized as follows. 
In the next section, we describe our computational framework for interpreting generalizations and our precise model for endorsing such statements (i.e., a model of truth judgments).
To illustrate how the model works, we then work through a number of standard examples from the linguistics literature that any model of generics should be able to accomodate.
The third section discusses the relationship of our model to previous accounts of generics from the linguistics and philosophical literatures. 
These theoretical sections are followed by three empirical case studies: generalizations about categories (*generic language*), events (*habitual language*), and causes (*causal language*). 
In the case study of generics, we use measure relevant background knowledge and prevalence to predict endorsements of familiar generic statements (e.g., "Robins lay eggs").
In the study of habituals, we measure background knowledge but manipulate the prevalence or frequency of the event to predict endorsements of habitual statements about novel agents (e.g., "John runs" given that he's run a certain number of times in the past).
In this case study, we also further examine the nature of the relevant probabilities for endorsing generalizations, asking whether it matters how often John has run in the past (past frequency) or how often a speaker expects him to run in the future (predictive probability).
Finally, in our last case study, we manipulate background knowledge to show its causal influence on endorsing generalizations about novel causal events (e.g., "Herb X makes wugs sleepy"). 
We compare our model to two previously articulated quantitative models of generics as well as a lesioned-version of our model.
In all cases, we find a very strong agreement of our model's predictions to human elicited endorsements, where the simpler models fall short.
We conclude our paper by clarifying some of the theoretical claims of the model and discuss open-questions for this approach.

@@

The language of generalization is easy to spot when a property, that could apply to an individual, is predicated of a category (e.g., "Dogs have four legs": *has four legs* could apply to an individual as in "This dog has four legs").
In the semantics literature on generics, bare plural sentences of this kind are sometimes described as *characterizing sentences* in contrast with *kind-denoting* sentences where the property can only meaningfully apply to the category as a whole (e.g., "Dinosaurs are extinct"; *extinct* cannot apply to an individual dinosaur).
<!-- Dinosaurs are exctinct ~ John is a smoker? -->
Generalization can also manifest when describing instances of an individual [*habitual language*; e.g., "John smokes"; @Carlson1977; @Carlson2005]; in this case, the particular instance being generalized is an instance of an individual (e.g., John at a particular moment in time), which also permits predication (e.g., "John smoked yesterday after dinner").
Verbs like *causes* or *makes* also seem to convey generalization, in this case, about an instance of an actual causal event (*causal language*; e.g., "Fire causes smoke"). 
Psychologists, linguists, and philosophers have long studied the language of generalization, as it appears very simple (e.g., syntactically) yet its meaning is difficult to formalize.^[
  We further distinguish the problem of formalizing a *meaning* for the language of generalization as opposed to the problem of *identifying* generalizations. 
  Syntax alone is neither necessary nor sufficient for a listener to know that the sentence conveys a generalization  (e.g., indefinite singulars can encode generalizations: "A dog has four legs" and bare plurals may not: "Dogs are on my front lawn").
  Our analysis thus begins once a sentence has been disambiguated as conveying a generalization. 
]

The basic intuition behind our account is that before a listener hears a novel generalization such as "Alligators grow to be 10-feet long", they do not know how widely distributed the property to be in the category, including whether or not it is present at all.
The utterance provides a vague sense of how strongly the generalization applies (e.g., how many alligators grow to be 10-feet long), which the listener derives from their knowledge of how the property (*growing to be 10-feet long*) is distributed among other categories (e.g., other animals).
The decision of whether or not to endorse the generalization is that of a speaker reasoning about how well the utterance would align their interlocutor's beliefs about the prevalence of the feature in the category with those of their own.
We formalize this intuition in a truth-conditional semantics incorporated into a Bayesian model of belief updating.
<!-- We now the lay out the formal specification of this account along with theoretical justification. -->

### Interpretation model

@@

The model in Eq \ref{eq:L0} describes a general mechanism of belief-updating via an uncertain threshold semantics.
The semantic scale is determined by the prevalence prior $P(p)$.
For generalizations about categories (i.e., generic statements), $P(p)$ ranges over $[0, 1]$; $p$ denotes the chance that an instance of a category has a Boolean property.
To apply this same model to generalizations about events (i.e., habituals like “John runs”), we use a different, but related, scale: the frequency within a given time window (e.g., number of times John went for a run in the past week).^[
  This measure is closely related to the instantaneous probability density of the event, as the time window gets infinitesimally small.
]
For events then, $p$ is a rate and $P(p)$ ranges over $[0, \infty)$.

<!-- We thus define the scale for habituals to be over the probability density, or temporal frequency, of the event; the support of $P(p)$ would this case would be -->
<!-- must compute a probability distribution from the occurrence of events (e.g., a person going for a run). -->
<!-- One straightforward way is to compute the rate of the event with respect a certain time window (e.g., a day).  -->
<!-- The probability density of the event occurring in the window is proportional to the rate of the event occurring (e.g., number of times per week).^[ -->
<!-- For example, if John drinks tea on average four times a week and coffee seven times a week, the relative probability densities of him completing the actions on any given day is $\frac{4}{7}$ and 1, respectively. -->
<!-- ] -->

<!-- For events, the implicit generative model is a Poisson model in which events occur randomly in time. -->
<!-- The probability density of an event occurring at a particular time is governed by the rate parameter for the Poisson model.  -->
<!-- Thus, Eq. \ref{eq:L0} becomes a model of habitual interpretation (e.g., "John runs") if we take the underlying semantic scale to be that of the temporal frequency of an event (e.g., how often we expect an event to occur); the support of $P(p)$ is this case would be $[0, \infty]$. -->

@@

<!-- The endorsement model defined in the previous section predicts that the variability in endorsements for generic statements and other sorts of generalizations in language can be attributed to two factors: (i) the referent prevalence in the category under discussion $p$ in Eq. \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences---the prevalence prior---$P(p)$ (Eq. \ref{eq:L0}). -->
We explore the predictions of the endorsement model in the context of a few worked examples.
These examples are taken from the linguistics literature on generics and are statements that have been historically challenging for prevalence-based approaches (see Table 1).
We implemented these and all subsequent Bayesian models in the probabilistic programming language WebPPL [@dippl].
All models, analyses, data and links to experiments used in this paper can be found at \url{https://github.com/mhtess/genlang-paper}.

Endorsement predictions depend upon the uncertain threshold model's interpretations, which are highly sensitive to background knowledge.
Background knowledge may be richly structured, reflecting intuitive theories about the underlying causes of different kinds of properties [cf., @Leslie2007].
This model posits, however, that the only impact of structured knowledge on truth judgments is in their implications for beliefs about prevalence, formalized in terms of a prevalence prior $P(p)$. 
<!-- \ndg{i’d save this for expt sections, and here just say that we posit intuitive priors for illustrations and introduce a method to actually elicit them below} -->
<!-- \mht{without this, we don't have an explanation for what the prevalence prior is, which is important for understanding the examples... i removed stuff about Betas, but check this again...} -->
The prevalence prior reflects a listener's beliefs about the prevalence of the feature in an unknown or unfamiliar category and be conceptualized in a theory-neutral way as a distribution over the prevalence among alternative categories (Figure\ \@ref(fig:simulations)).^[
  Alternatively, the prevalence prior can be conceptualized as a marginal distribution on prevalence derived from an intuitive theory formalized in a probabilistic language of thought [e.g., @Goodmanconcepts]. 
]
<!-- For example, think about five of your favorite kinds of animal: What percentage of each of them *are female*? What percentage of each of them *lay eggs*? -->
For example, the *lay eggs* prevalence prior should be bimodal, with substantial probability mass near 0-prevalence (since many animal categories do not have egg-layers) and a secondary component peaked around 0.5 (because among the animals with egg-layers, only the female members of the category have the property).
Conversely, the distribution over the prevalence of *being female* is unimodal and centered at 50%-prevalence, because almost all animals have female members in that proportion.
Figure\ \@ref(fig:simulations) (row 1) shows these and other intuitive prevalence priors for different properties (we introduce methods for empirically eliciting these priors in the experimental section).
We now turn our attention to the endorsement model's predictions.

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  Example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Robins lay eggs",
              "4. Robins are female",
              "5. Mosquitos carry malaria", 
              "6. Sharks don't eat people",
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%",  "50%", "50%", "5%", "85%", "0 times", "100%", "50%/50%"),
  `intuitive truth value` = c(
    "True", "False",  "True", "False",
    "True", "False","True", "False", "True" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Only female robins (50%) lay eggs",
    "Same number that lay eggs (50%)",
    "Very few mosquitos actually carry malaria",
    "Most sharks don't eat people",
    "Consider there has never been any mail from Antarcita",
    "Consider 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia, and no individual elephant lives in both Africa and Asia"
  )
) %>%
  rename("Intuitive referent prevalence" = referent.prevalence,
         "Intuitive truth value" = intuitive.truth.value,
         "Issue" = potential.issue)

worked.examples.tab <- xtable::xtable(worked.examples, 
                       caption = "Example sentences that a theory of the language of generalizations should correctly predict. See details of each example in corresponding section.", 
                       align=c('| p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))

@@

## Relation to intuitive theories

Our theory assumes that listeners and speakers employ real-world knowledge of objects and events in order to use and interpret generalizations.
It is this real-world knowledge (presently formalized in terms of a prevalence prior) where issues about domain specific beliefs, interpretation of properties [@Prasada2006], over-hypotheses [@Leslie2008], and essentialism [@Gelman2003] can all play a role.
<!-- It was not our present goal to model this aspect of interlocutors' conceptual knowledge. -->
<!-- Instead,  -->
We hypothesize that all of this knowledge feeds into participants' predictions, measured through judgments about prevalence.
That is, even though our underlying semantics is defined in terms prevalence of individual properties, this does not imply that the concepts involved in generic language understanding are defined merely by their properties. 
Instead, complex intuitive theories [that may reflect, for example conceptual role, see @Goodmanconcepts] give rise to prevalence priors, which then yield generic judgements.
<!-- which we model in a precise, quantitative manner. -->
This framework, thus, brings precision and clarity to the *output* of these cognitive processes and conceptual understanding: intuitions about prevalence.
Applying the same precision and clarity to the more abstract aspects of conceptual knowledge including property knowledge, essentialism, etc. is an important next step for this line of work.
Probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts] are obvious starting places to look for such a formalism for conceptual structure and higher-order abstractions.

@@

Conceptual knowledge concerning the strikingness or dangerousness of properties and their relation to generic language has been of particular interest to psychologists and philosophers since @Leslie2007.
We described before that the strikingness of certain properties plausibly influences prevalence priors or a speaker's predictions about future prevalence.
We have collected pilot data suggesting these constructs are indeed altered as a result of introducing information about the dangerousness of features to participants [e.g., as in @Cimpian2010].
More empirical work is needed to understand whether and how strikingness influences generic understanding above and beyond the probabilistic constructs we have posited in our theory.
<!-- If such effects exist, our modeling framework could be elaborated with a non-informational speaker utility [see e.g., @Yoon2016; @Yoon2017]. -->
